%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\makeatletter
%\renewcommand\thesection{}
%\renewcommand\thesubsection{\@arabic\c@section.\@arabic\c@subsection}
\makeatother

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

%\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

%\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{booktabs}

\newcommand{\code}[1]{{\footnotesize\textsf{#1}}}
\newcommand{\q}[1]{``#1''}

\usepackage{listings}

\usepackage{geometry}
\geometry{letterpaper, margin=1.95cm}

\usepackage{url}

%\usepackage{multirow}


%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Utah State University, Computer Science Department} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge CS5890 Data Science - Project Proposal \\ Random Acts Of Pizza \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Team \textbf{Pizza Hackers}: Tam Nguyen and Hung Pham} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}
	
\maketitle
	
\section{Introduction}

In this proposal we will discuss our plan to perform data analysis on a social interaction dataset, where requester ask for free pizza on a Reddit community \q{Random Acts of Pizza}\footnote{\url{https://www.reddit.com/r/Random_Acts_Of_Pizza/}}. We will discuss the social interaction problems, the dataset provided by Kaggle, preliminary of our analysis plan, which data science toolkits we plan to use.

\section{The team: Pizza hackers}

We name our team \q{Pizza hackers} in direct references to the task that we want to tackle, and our Computer Scientist's root. \q{Pizza hackers} consists of two members: Tam Nguyen and Hung Pham. Tasks such as implementations of data analysis experiments, report writing, and visualization will be divided among team members. All members will be involved in analysis of experiments results as well as any decision in term of project direction.

\input{problem}

\input{data}

\input{plan}

\input{toolkit}

\begin{thebibliography}{10}

\bibitem{tim14}
Tim Althoff, Cristian Danescu-Niculescu-Mizil, Dan Jurafsky.
\emph{How to Ask for a Favor: A Case Study on the Success of Altruistic Requests},
Proceedings of ICWSM,
2014.

\bibitem{word2vec}
Tomas Mikolov, Ilya Sutskever, Kai Chen, Greg S Corrado, Jeff Dean.
\emph{Distributed representations of words and phrases and their compositionality},
Advances in neural information processing systems,
2013.


\end{thebibliography}

\end{document}